% Introduction section expanded for the moderate-length revision.
% This file is a section fragment, not a standalone LaTeX document.

\section{Introduction}
\label{sec:introduction}

CNN deployment on edge devices is constrained by memory footprint, arithmetic cost, and power budget. Quantization is a common compression approach because it represents weights and activations with low-precision numerical formats instead of full-precision floating-point values \cite{gholami2021survey,nagel2021whitepaper,krishnamoorthi2018quantizing}. When suitable low-precision kernels are available, quantization can reduce storage and arithmetic requirements. This paper is motivated by that deployment direction, but it studies only simulated PTQ behavior and does not report measured hardware speedup.

Post-training quantization (PTQ) is attractive because it starts from an already trained FP32 model and determines quantization parameters during calibration. Compared with quantization-aware training, PTQ avoids retraining the full network and is easier to integrate into a deployment pipeline \cite{nagel2021whitepaper}. However, PTQ accuracy depends strongly on calibration quality. This dependence becomes more important as the activation bit-width decreases, because each scale and clipping decision affects fewer representable integer levels.

Aggressive INT4 activation quantization makes PTQ especially sensitive to calibration choices. With only 4-bit activation values, the quantizer must cover both common activation values and rare large values. If the calibration range is too wide, many common values are represented with coarse steps. If the range is too narrow, large values are saturated. Prior low-bit PTQ studies therefore show that 4-bit quantization is more difficult than the more standard 8-bit case \cite{banner2018post,choukroun2019low,nahshan2019loss}.

Activation outliers are an important source of this difficulty. In post-ReLU activations, rare large values can dominate MinMax calibration and expand the quantization range. This reduces the effective resolution assigned to the bulk of the activation distribution. Activation clipping and outlier-handling methods have been studied as ways to reduce this sensitivity, including learned activation clipping and explicit outlier manipulation \cite{choi2018pact,zhao2019outlier,xiao2022smoothquant}. In the evaluated setting, clipping trades limited saturation of large values for lower rounding error over common activation values.

This paper studies a calibration-time clipping rule for simulated INT4 PTQ, called Layer-wise MSE-Selected Activation Clipping. For each post-ReLU activation site, the method evaluates a predefined set of percentile thresholds and selects the candidate with the lowest activation reconstruction MSE. The search is discrete and restricted to the candidate set; it is not a continuous global optimization of the clipping threshold. The activation MSE criterion is also local to calibration activations, so it should not be interpreted as a direct optimization of final test accuracy.

The scope of this paper is intentionally controlled. We evaluate simulated PTQ on CIFAR-10 using a CIFAR-style ResNet-18 model and compare FP32, INT8-MinMax, INT4-MinMax, INT4-P99.9, and INT4-MSE-Selected. The implementation uses fake quantization and dequantization to study accuracy and reconstruction error. It does not report real hardware latency or deployment speedup. The main contributions are:
\begin{itemize}
    \item a controlled simulated PTQ pipeline for CIFAR-10 ResNet-18 quantization;
    \item an implemented layer-wise MSE-selected clipping rule for INT4 post-ReLU activation quantization;
    \item an analysis of accuracy, reconstruction error, logit consistency, and layer-wise clipping behavior under the implemented baselines.
\end{itemize}
