\section{Method}
\label{sec:method}

\subsection{Overview}
\label{subsec:method_overview}
This work studies a post-training quantization (PTQ) pipeline for a CIFAR-10 ResNet-18-CIFAR classifier. The central method is Layer-wise MSE-Selected Activation Clipping, which determines the activation clipping threshold of each observed post-ReLU activation site from calibration data. The method is compared with MinMax calibration and fixed percentile clipping within the same simulated quantization framework.

The proposed method is a calibration-time PTQ method. The floating-point model is first trained, and the quantization procedure is then applied without back-propagation, gradient updates, or retraining. All calibration passes are performed in evaluation mode and under a no-gradient setting. Therefore, the experiments in this paper should be interpreted as simulated PTQ with fake quantization rather than quantization-aware training (QAT). In particular, the implementation does not use a real INT4 inference kernel; instead, it replaces weights with their quantized--dequantized values and inserts activation fake-quantization operations at the selected activation sites.

\subsection{Quantization Setting}
\label{subsec:quant_setting}
Let $W_l$ denote the weight tensor of a convolutional or fully connected layer $l$, and let $a_l$ denote the output tensor of a post-ReLU activation site. The INT4 experiments use signed symmetric per-channel weight quantization and unsigned post-ReLU activation quantization. For a weight output channel $c$, the dequantized simulated INT4 weight is computed as
\begin{equation}
\hat{W}_{l,c}
= s^w_{l,c} \cdot
\mathrm{clip}\left(
\mathrm{round}\left(\frac{W_{l,c}}{s^w_{l,c}}\right),
-7, 7
\right),
\end{equation}
where $s^w_{l,c}$ is determined from the maximum absolute value of that output channel. This corresponds to a signed INT4 integer range of $[-7,7]$.

For post-ReLU activations, all observed activation values are non-negative. Therefore, the activation fake-quantizer uses an unsigned INT4 range $[0,15]$, a clipping interval $[0,\alpha_l]$, and zero point $z^a_l=0$. Given a clipping threshold $\alpha_l$, the activation scale is
\begin{equation}
s^a_l = \frac{\alpha_l}{15},
\end{equation}
and the simulated quantized--dequantized activation is
\begin{equation}
\hat{a}_l
= s^a_l \cdot
\mathrm{clip}\left(
\mathrm{round}\left(
\frac{\mathrm{clip}(a_l,0,\alpha_l)}{s^a_l}
\right),
0,15
\right).
\label{eq:activation_fake_quant}
\end{equation}
This fake-quantization operation is applied per tensor for each observed ReLU module. Thus, different ReLU modules may have different activation clipping thresholds and scales, but each module uses one scalar activation scale.

The full paper considers the following configurations: an FP32 reference, an INT8-MinMax sanity-check baseline, an INT4-MinMax baseline, an INT4 fixed-percentile clipping baseline, and the proposed INT4-MSE-Selected method. The INT8-MinMax baseline uses per-channel symmetric INT8 weights and per-tensor UINT8 activations at convolution and linear outputs. The INT4 variants use per-channel symmetric INT4 weights and per-tensor-per-ReLU UINT4 activations at post-ReLU sites. The INT4 activation methods differ only in how the upper clipping threshold $\alpha_l$ is selected.

\subsection{MinMax Calibration}
\label{subsec:minmax_calibration}
MinMax calibration is the default INT4 activation baseline. During calibration, forward hooks are registered on all named ReLU modules. For each post-ReLU activation site $l$, the observer records the largest activation value seen over the calibration batches. The clipping threshold is then set as
\begin{equation}
\alpha^{\mathrm{MM}}_l
= \max_{x \in \mathcal{D}_{\mathrm{cal}}}
\max a_l(x),
\end{equation}
where $\mathcal{D}_{\mathrm{cal}}$ is the calibration subset and $a_l(x)$ denotes the post-ReLU activation tensor produced by input $x$. The resulting threshold is used to construct the UINT4 activation scale in (2), and the activation is fake-quantized according to (3).

This calibration rule preserves the largest observed activation in the calibration data. However, it also uses the full quantization range to cover rare large activation values. The present paper uses this rule as the main INT4 PTQ baseline and does not modify the model by retraining.

\subsection{Fixed Percentile Clipping}
\label{subsec:fixed_percentile_clipping}
Fixed percentile clipping replaces the maximum observed activation with a predefined percentile of the collected calibration activations. For each post-ReLU activation site $l$, the calibration activations are detached, moved to the CPU, flattened, and concatenated across calibration batches. Let $v_l$ denote this one-dimensional collection of activation values. Given a fixed percentile $p$, the clipping threshold is
\begin{equation}
\alpha^{p}_l = \mathrm{Percentile}(v_l,p).
\end{equation}
The fixed-percentile baseline in this project uses $p=99.9$. After $\alpha^p_l$ is selected, the same UINT4 fake-quantization rule in (3) is used. Therefore, fixed percentile clipping changes only the calibration rule for the activation upper bound and keeps the weight quantization, activation integer range, and activation fake-quantization formula unchanged.

\subsection{Layer-wise MSE-Selected Activation Clipping}
\label{subsec:mse_selected_clipping}
The proposed method selects the clipping threshold separately for each observed post-ReLU activation site. Instead of using one fixed percentile for all layers, it evaluates a small candidate percentile set
\begin{equation}
\mathcal{P} = \{99.0, 99.5, 99.9, 99.95, 100.0\}.
\end{equation}
For each layer $l$ and each candidate percentile $p \in \mathcal{P}$, the method computes a candidate clipping threshold
\begin{equation}
\alpha_l(p) = \mathrm{Percentile}(v_l,p),
\end{equation}
where the $100.0$ percentile corresponds to the maximum observed calibration activation. The collected activations $v_l$ are then fake-quantized and dequantized by (3) using $\alpha_l(p)$. The activation reconstruction error for candidate $p$ is measured as
\begin{equation}
\mathrm{MSE}_l(p)
= \frac{1}{N_l}\sum_{i=1}^{N_l}
\left(v_{l,i} - \hat{v}_{l,i}(p)\right)^2,
\end{equation}
where $N_l$ is the number of collected activation elements for layer $l$, and $\hat{v}_{l,i}(p)$ is the fake-quantized and dequantized activation value under candidate percentile $p$.

The selected percentile and clipping threshold are
\begin{equation}
p_l^* = \arg\min_{p \in \mathcal{P}} \mathrm{MSE}_l(p),
\qquad
\alpha_l^* = \alpha_l(p_l^*).
\end{equation}
The selected $\alpha_l^*$ is then used to construct the final activation quantization parameters for that ReLU module.

It is important to emphasize that this method is MSE-selected only within the predefined candidate percentile set $\mathcal{P}$. It is not a continuous-space global optimization method, and it does not claim to find the globally optimal clipping threshold. The method only performs a finite calibration-time search over the candidate percentiles listed above.

\subsection{Algorithm or Pseudocode}
\label{subsec:algorithm}
The calibration procedure for Layer-wise MSE-Selected Activation Clipping is summarized below.

\begin{figure}[t]
\footnotesize
\begin{minipage}{\linewidth}
\hrule
\vspace{0.4em}
\textbf{Pseudocode 1: Layer-wise MSE-Selected Activation Clipping}
\vspace{0.4em}
\hrule
\vspace{0.4em}
\textbf{Input:} FP32 model $f$, calibration loader $\mathcal{D}_{\mathrm{cal}}$, candidate percentile set $\mathcal{P}=\{99.0,99.5,99.9,99.95,100.0\}$, activation integer range $[q_{\min},q_{\max}]=[0,15]$.\\
\textbf{Output:} Layer-wise activation quantization parameters $\{\theta_l\}$.
\begin{enumerate}
    \item Set $f$ to evaluation mode and disable gradient computation.
    \item Find all named ReLU modules and treat their outputs as post-ReLU activation sites.
    \item Register a forward hook on each observed ReLU module.
    \item For each calibration batch, run a forward pass and collect detached post-ReLU outputs.
    \item Remove all forward hooks after calibration data collection.
    \item For each observed activation site $l$:
    \begin{enumerate}
        \item Concatenate and flatten the collected activations into $v_l$.
        \item For each candidate percentile $p \in \mathcal{P}$:
        \begin{enumerate}
            \item Compute $\alpha_l(p)=\mathrm{Percentile}(v_l,p)$.
            \item Build UINT4 post-ReLU activation parameters using $[0,\alpha_l(p)]$ and $[0,15]$.
            \item Fake-quantize and dequantize $v_l$ using these parameters.
            \item Compute $\mathrm{MSE}_l(p)$ between the original and dequantized activations.
        \end{enumerate}
        \item Select $p_l^*=\arg\min_{p\in\mathcal{P}}\mathrm{MSE}_l(p)$.
        \item Store the final layer-wise activation parameters $\theta_l$ using $\alpha_l^*=\alpha_l(p_l^*)$.
    \end{enumerate}
    \item Attach activation fake-quantization wrappers to the corresponding ReLU modules for simulated INT4 PTQ inference.
\end{enumerate}
\vspace{0.2em}
\hrule
\end{minipage}
\caption{Pseudocode for calibration-time MSE-selected activation clipping.}
\label{alg:mse_selected_clipping}
\end{figure}

After calibration, the selected activation parameters are fixed during evaluation. No labels are used in the clipping search, and no training objective is optimized. The search criterion is purely the layer-wise activation reconstruction MSE on calibration activations.