% Related Work section draft using entries from paper/refs.bib.
% This file is a section fragment, not a standalone LaTeX document.

\section{Related Work}
\label{sec:related_work}

\subsection{Post-training Quantization}
\label{subsec:related_ptq}

Post-training quantization (PTQ) reduces the numerical precision of a trained neural network after training, without updating the model parameters through back-propagation. Compared with quantization-aware training, PTQ is attractive when training data, training budget, or retraining time is limited. General surveys and white papers describe common PTQ components such as calibration, affine quantization, symmetric quantization, scale and zero-point computation, and fake-quantized evaluation \cite{gholami2021survey,nagel2021whitepaper,krishnamoorthi2018quantizing}. Integer-only inference further motivates practical quantization schemes that map floating-point tensors to low-precision integer ranges for efficient deployment \cite{jacob2018quantization}. However, PTQ accuracy depends strongly on the chosen calibration strategy, especially for activation quantization.

Recent PTQ methods also show that calibration can be formulated as an error minimization problem rather than only as direct MinMax range collection. AdaRound studies adaptive weight rounding for PTQ, while BRECQ uses block reconstruction to improve low-precision post-training quantization \cite{nagel2020adaround,li2021brecq}. These works indicate that calibration-time reconstruction objectives can be useful for reducing quantization error. In contrast, this paper keeps the calibration procedure simpler and focuses on selecting post-ReLU activation clipping thresholds from a finite percentile set.

\subsection{Low-bit Quantization for CNNs}
\label{subsec:related_low_bit_cnn}

Low-bit quantization further reduces precision below the widely used 8-bit setting. For CNNs, reducing weight and activation precision can lower memory footprint and simplify inference arithmetic, which is attractive for edge deployment. Nevertheless, INT4 quantization is more sensitive than INT8 quantization because only a small number of representable levels are available. This limited resolution makes the choice of quantization scale and clipping range more important. Prior work has investigated low-bit quantization and post-training 4-bit quantization for convolutional networks, showing both the potential efficiency benefit and the increased accuracy risk of aggressive precision reduction \cite{banner2018post,choukroun2019low}.

The sensitivity of INT4 PTQ is especially relevant for activation quantization. Weight quantization can often use per-channel symmetric scaling, whereas activation distributions depend on input data and can vary across layers. As a result, a single calibration rule may not be equally suitable for all activation sites. This motivates the layer-wise design used in this work, where each post-ReLU activation site selects its own clipping threshold under the same candidate percentile set.

\subsection{Activation Clipping and Outlier Suppression}
\label{subsec:related_activation_clipping}

Activation outliers are a major source of error in low-bit activation quantization. Under MinMax calibration, rare large activation values can determine the full quantization range. This increases the quantization step size and may reduce the effective resolution for the majority of activation values. Activation clipping addresses this issue by selecting a smaller upper bound for the activation range. The resulting threshold introduces a trade-off between clipping error on large values and rounding error on common values. Prior studies have explored activation clipping and outlier handling from different perspectives, including parameterized activation clipping and outlier channel splitting \cite{choi2018pact,zhao2019outlier}. PyTorch's MinMaxObserver also reflects the common baseline practice of collecting extrema from calibration data to determine quantization parameters \cite{pytorch_minmaxobserver}.

The method studied in this paper follows the general direction of activation clipping and outlier suppression, but it is intentionally conservative. It does not introduce learnable clipping parameters or retraining. Instead, it collects calibration activations from a trained CNN and selects each post-ReLU activation threshold from a predefined percentile candidate set according to activation reconstruction MSE. This makes the method layer-wise and data-dependent while keeping it within a simulated PTQ setting.
